New approaches for boosting to uniformity

### 2014-09-22 assets/paperdraft/parts/approaches.tex
Major textual changes to the section on uniformity metrics.
nothing

% TODO sign

@@

TODO give explanations here

>>>>

@@

Explanation:
\begin{multline*}
	- \dfrac{\partial} {\partial \, \score_i} \FL = 
		- \binIweight \frac{\partial }{ \partial \, \score_i} \int \abs{F_{\bin(i)}(x) - F(x)}^p dx = \\
	= \binIweight \abs{F_{\bin(i)}(x) - F(x)}^p \bigg|_{x=\score_i-}^{x=\score_i+} = \\
	= \{ \text{assuming that $F_{\bin(i)}(x)$, $F(x)$ changed small } \} = \\
	= \binIweight p \abs{F_{\bin(i)}(x) - F(x)}^{p-1} \sgn(F_{\bin(i)}(x) - F(x)) \left[F(x-) - F(x+) + F_{\bin(i)}(x+) - F_{\bin(i)}(x-)\right] \bigg|_{x=\score_i}= \\
	= \binIweight p \abs{F_{\bin(i)}(x) - F(x)}^{p-1} \sgn(F_{\bin(i)}(x) - F(x)) \left[- \frac{w_i}{\sum_j w_j} + \frac{w_i}{\binIweight} \right] \bigg|_{x=\score_i}= \\
	= \{ \text{ignoring $\frac{w_i}{\sum_j w_j}$}  \}
	\cong \binIweight \, p \,  \abs{F_{\bin(i)}(x) - F(x)}^{p-1} 
	% 	\sgn[F_{\bin(i)}(x) - F(x)]
	% 	\dfrac{w_i}{\binIweight}
	% 	\Bigg|_{x=\score_i} = \\
	% = 
	% 	w_i \, p \,  \abs{F_{\bin(i)}(x) - F(x)}^{p-1}
	% 	\sgn[F_{\bin(i)}(x) - F(x)]
	% 	\Bigg|_{x=\score_i}
\end{multline*}
